Exp1 - Opt w_max and {A,phi)

### 2018-01-31 voltagebudget/analysis/paper_figures.Rmd
Added intial/cartoon PLC opt model figures

```{r, fig.width=1.5, fig.height=1}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
  theme_classic()
```
```{r, fig.width=0.4, fig.height=0.8}
vms %>% 
  filter(t > 0.25, t < 0.27) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())
  # theme_classic()
```

>>>>

```{r, fig.width=1.5, fig.height=1}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
  theme_classic()
```

```{r, fig.width=0.4, fig.height=0.8}
vms %>% 
  filter(t > 0.25, t < 0.27) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())
  # theme_classic()
```

# Optimal PLC

```{r, message=FALSE}
plc_spikes <- read_csv("plc_spikes.csv")
plc_traces <- read_csv("plc_traces.csv")
```

```{r, fig.width=0.6, fig.height=1}
plc_spikes %>% 
  ggplot(aes(x=ts_opt, y=n)) + 
  geom_point(color="black", size=0.8) +
  geom_point(data=filter(plc_spikes, ts != ts_opt), aes(x=ts, y=n), color="red", size=1.5, shape=4, alpha=0.6) +
  xlim(0.2, 0.24) +
  theme_classic() +
  # labs(x="Time (s)", y="N") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major.y=element_blank(),
      panel.grid.minor.y =element_blank(),
      plot.background=element_blank()) -> p1
```

```{r, fig.width=1.2, fig.height=1}
plc_traces %>% 
  ggplot(aes(x=variances, y=errors)) +
  geom_line() +
  theme_classic() +
  ylab("Errors (s)") +
  xlab("Variance (s)") -> p2
```

```{r, fig.width=2.25, fig.height=1}
plot_grid <- rbind(c(1, 1, NA, 2, 2, 2),c(1, 1, NA, 2, 2, 2),c(1, NA, NA, 2, 2, 2))
grid.arrange(p1, p2, layout_matrix=plot_grid)
```
